```{r, echo=FALSE}
#| include: false
out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
source("_common.R")
```
# Usage environment {#sec-usage-environment }

Please refer to the output results of `quato check`.

* quarto is using the released version 1.5.57.
* R is version 4.4.0
* I use luaLatex for output in Japanese. I have installed MacTex because TinyTex doesn't include it.
* It may be better to uninstall TinyTex.
* I have set it to use `lightbox` extension ( included in Quarto v1.4+.)


```{.sh}
# Quarto check output
Quarto 1.5.57
[✓] Checking versions of quarto binary dependencies...
      Pandoc version 3.2.0: OK
      Dart Sass version 1.70.0: OK
      Deno version 1.41.0: OK
      Typst version 0.11.0: OK
[✓] Checking versions of quarto dependencies......OK
[✓] Checking Quarto installation......OK
      Version: 1.5.57
      Path: /Applications/quarto/bin

[✓] Checking tools....................OK
      TinyTeX: (not installed)
      Chromium: (not installed)

[✓] Checking LaTeX....................OK
      Using: Installation From Path
      Path: /usr/local/texlive/2024/bin/universal-darwin
      Version: 2024

[✓] Checking basic markdown render....OK

[✓] Checking Python 3 installation....OK
      Version: 3.12.7
      Path: /Users/tk4o2ka/github/tinderboxwithquarto/.venv/bin/python3
      Jupyter: 5.7.2
      Kernels: python3

[✓] Checking Jupyter engine render....OK

[✓] Checking R installation...........OK
      Version: 4.4.0
      Path: /Library/Frameworks/R.framework/Resources
      LibPaths:
        - /Library/Frameworks/R.framework/Versions/4.4-arm64/Resources/library
      knitr: 1.46
      rmarkdown: 2.26

[✓] Checking Knitr engine render......OK
```


## RStudio Session information { #sec-session-information }
```{r}
#| echo: false
sessionInfo()
```


## installed packages { #sec-installed-packages }

```{r}
#| echo: false
#| message: false
pacman::p_load(tidyverse, gt)
installed.packages() |> 
  as_tibble() |> 
  select(Package, Version, Built) |> 
  gt::gt()
```



